\section{Project Plan}

\subsection{Proposed Solution / Methodology}
% >摆你“系统流”（screen/audio→VLM→LLM/agentic→MCP-style skill bus→GUI→safety），只讲结构与模块边界，不承诺训练细节。

\subsection{Experimental Design}
% >把你在文献里对“评测协议（evaluation protocols）/指标（metrics）/场景（scenarios）”的回顾，转成计划性的评测设计（谁、在什么任务、用哪些指标判定“成功”）。这是模板专门的栏目。

\subsection{Expected Results}
% >非常适合“产品向”——列可交付物（prototype、代码、评测脚本、演示视频、文档）+ “达到即视为成功”的阈值性指标（success criteria）。

\subsection{Progress Analysis and Gantt Chart}
% >补一个甘特图与里程碑（milestones），并配风险与伦理—评分细则这里有明确加分点（Gantt、里程碑、风险/伦理完备）。

\subsubsection{Risk \& Ethics}


\paragraph{Project Objectives}
The primary objectives of this project are as follows:

\begin{enumerate}
    \item Develop a fully functional real-time prototype based on the GCC approach, capable of event detection, strategy suggestions, and voice loop interaction.
    
    \item Implement an MCP-style modular orchestration system that integrates skills, planning, memory, and reflection, enabling a plug-and-play architecture.
    
    \item Define clear, reproducible evaluation metrics to assess the system’s performance, including metrics such as \textit{pass@k}, \textit{Invalid\%}, and \textit{macro-micro performance}.
\end{enumerate}

\paragraph{Expected Deliverables}
The following deliverables will be provided at the end of the project:

\begin{enumerate}
    \item \textbf{System Prototype}: A fully functional prototype that includes:
    \begin{itemize}
        \item Screen capture and lightweight perception.
        \item Agentic modules for event detection, strategy suggestion, and voice loops.
        \item MCP-style skill bus for modular integration and execution.
        \item GUI executor for interacting with the game interface.
        \item Safety safeguards, including confirmation features.
    \end{itemize}
    
    \item \textbf{Evaluation Scripts and Configuration}: Reproducible task scripts and configuration files that include:
    \begin{itemize}
        \item Metrics for performance tracking.
        \item Logging and auditing tools for system comparison.
    \end{itemize}
    
    \item \textbf{User Documentation and Demos}: Comprehensive documentation and demo materials, including:
    \begin{itemize}
        \item Quick start guides and configuration templates.
        \item Demo videos showcasing system capabilities.
    \end{itemize}
\end{enumerate}